Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-05 paper.tex
incorporada nova figura de symetria e clustering coef

%\begin{figure*} 
%	\centering
%	\includegraphics[width=.6\textwidth,height=10cm]{figs/im13PCAPLOT_}
%	\caption{The first plot shows degree versus clustering coefficient, a well known pattern characterized by the high clustering being more incident in vertices with lower degrees.
%		In the second plot, the abscissas is an average of centrality metrics, an intermediary plot to ease understanding.
%		The third plot exhibits the greater dispersion of the symmetry-related ordinates.
%		This greater dispersion suggests that symmetry-related metrics are more powerful, with respect to dispersion,
%		for characterizing interaction networks than the clustering coefficient,
%		especially for hubs and intermediary vertices.
%		This figure was obtained with a snapshot of the LAU list in a window size of $ws = 1000$ messages.
%		Similar structures were observed in all window sizes $ws\;\in\;[500,10000]$, in networks derived from email lists,
%		and in networks from Facebook, Twitter and Participabr,
%		which suggests a common relationship between the metrics of degrees, strengths and betweenness centrality,
%		the symmetry-related metrics and clustering coefficient.}
%	\label{fig:sym}
%\end{figure*}

@@

%Within networks as the whole objects of analysis,
%we were able to observe a peculiar correlation pattern 
%between the number of threads and the number of participants.
\begin{figure}
   \centering
   \includegraphics[trim={0 0 0 1cm},clip,width=\columnwidth]{figs/mpgamma____________}
	\caption{A scatter plot of number of messages $M$ versus number of participants $N$ versus number of threads $\Gamma$ for 140 email lists.
Highest $\Gamma$ are associated with low $N$.
The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise.
This negative correlation between $N$ and $\Gamma$ can also be observed in Table~\ref{tab:genLists}.
Accordingly,
for $M=20000$ messages, this inflection
of correlation 
was found to be around $N=1500$
and LAU, LAD, MET lists 
present smaller networks.}
	\label{fig:nmgamma3d}
\end{figure}

>>>>

\begin{figure} 
	\centering
	%\includegraphics[width=.6\textwidth,height=10cm]{figs/im13PCAPLOT__}
	\includegraphics[width=.45\textwidth]{figs/im13PCAPLOT__}
	\caption{The first plot shows degree versus clustering coefficient, a well known pattern characterized by the high clustering being more incident in vertices with lower degrees.
		In the second plot, the abscissas is an average of centrality metrics, an intermediary plot to ease understanding.
		The third plot exhibits the greater dispersion of the symmetry-related ordinates.
		This greater dispersion suggests that symmetry-related metrics are more powerful, with respect to dispersion,
		for characterizing interaction networks than the clustering coefficient,
		especially for hubs and intermediary vertices.
		This figure was obtained with a snapshot of the LAU list in a window size of $ws = 1000$ messages.
		Similar structures were observed in all window sizes $ws\;\in\;[500,10000]$, in networks derived from email lists,
		and in networks from Facebook, Twitter and Participabr,
		which suggests a common relationship between the metrics of degrees, strengths and betweenness centrality,
		the symmetry-related metrics and clustering coefficient.}
	\label{fig:sym}
\end{figure}

@@

%Within networks as the whole objects of analysis,
%we were able to observe a peculiar correlation pattern 
%between the number of threads and the number of participants.
\begin{figure}
   \centering
   \includegraphics[trim={0 0 0 1cm},clip,width=.7\columnwidth]{figs/mpgamma____________}
	\caption{A scatter plot of number of messages $M$ versus number of participants $N$ versus number of threads $\Gamma$ for 140 email lists.
Highest $\Gamma$ are associated with low $N$.
The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise.
This negative correlation between $N$ and $\Gamma$ can also be observed in Table~\ref{tab:genLists}.
Accordingly,
for $M=20000$ messages, this inflection
of correlation 
was found to be around $N=1500$
and LAU, LAD, MET lists 
present smaller networks.}
	\label{fig:nmgamma3d}
\end{figure}
